
This chapter describes software related to GPSCV time-transfer.


\section{Software overview}

Time-transfer files are produced by \cc{mktimetx} from the GNSS receiver logs and counter/timer measurements.
The time-transfer files are in  RINEX observation  and CGGTTS format. 
Currently, CGGTTS-format files are only produced for GPS. 
Figure \ref{f:GPSCVProcessing} illustrates the processing chain TODO. 

The OpenTTP software suite is catalogued in Table \ref{t:OTTPSoftware}
\begin{table}
\begin{tabular}{l|l|l}
	& program & \\ 
	\hline
GPSCV processing  &  & \\
	& \hyperlink{h:mktimetx}{mktimetx} & core program\\
	& \hyperlink{h:runmktimetx}{runmktimetx.pl} & \\
	& \hyperlink{h:mkcggtts}{mkcggts.py} & \\
	\hline
TIC logging & & \\
	& \hyperlink{h:hp5313xlog}{hp5313xlog.pl} &\\
	& \hyperlink{h:cnt9xlog}{cnt9xlog.py} &\\
	& \hyperlink{h:okxemlog}{okxemlog.pl} & \\
	& \hyperlink{h:prs10log}{prs10log.pl} & \\
	& \hyperlink{h:ticclog}{ticclog.py} & \\
	\hline
GNSS receiver logging & & \\
	&	\hyperlink{h:jnslog}{jnslog.pl} & Javad\\
	& \hyperlink{h:nvslog}{nv08log.pl} & NVS\\
	& \hyperlink{h:restlog}{restlog.pl} & Trimble Resolution T\\
	& \hyperlink{h:ublox9log}{ublox9log.py} & ublox\\
	& \hyperlink{h:ubloxlog}{ubloxlog.pl} & ublox\\
GNSS receiver utilities & & \\
	& \hyperlink{h:jnsextract}{jnsextract.pl} & \\
	& \hyperlink{h:nv08extract}{nv08extract.pl} & \\
	& \hyperlink{h:nv08info}{nv08info.pl} & \\
	& \hyperlink{h:restextract}{restextract.pl} & \\
	& \hyperlink{h:restinfo}{restinfo.pl} & \\
	& \hyperlink{h:ubloxextract}{ubloxextract.py} & \\
	& \hyperlink{h:ubloxmkdev}{ubloxmkdev.py} & \\
	\hline
Analysis tools & & \\
	& \hyperlink{h:cggttsqc}{cggttsqc.py} & \\
	& \hyperlink{h:cmpcggtts}{cmpcggtts.py} & \\
	& \hyperlink{h:editcggtts}{editcggtts.py} & \\
	& \hyperlink{h:editrnxnav}{editrnxnav.py} & \\
	& \hyperlink{h:editrnxobs}{editrnxobs.py} & \\
	& \hyperlink{h:ticqc}{ticqc.py} & \\
Miscellaneous & & \\
  & \hyperlink{h:log1Wtemp}{log1Wtemp.pl} & \\ 
	\hline
\end{tabular}
\caption{GPSCV software overview \label{t:OTTPSoftware} }
\end{table}

\section{crontab \label{ss:crontab}}

Automatic logging, processing and archival of data is co-ordinated via the user \cc{cvgps}' \cc{crontab}.

A minimal \cc{crontab} for the user \cc{cvgps} looks like this:
\begin{lstlisting}
# Check that all logging is running every 5 minutes
*/5 * * * * /usr/local/bin/kickstart.pl # See ~/etc/kickstart.conf

# Run the processing of the data at 00:15
15 0 * * * nice $HOME/bin/runmktimetx.pl >/dev/null 2>&1 

# Give the processing some time to complete, then zip the files at 00:45
45 0 * * * nice $HOME/bin/gziplogs.pl >/dev/null 2>&1

# Check the status of the system once a day, just before the day rollover
56 23 * * * $HOME/bin/checkstatus.pl >$HOME/lockStatusCheck/status.dat
\end{lstlisting}
showing the three essential processes of logging, processing and archival of data.

The active crontab can be examined with the command \cc{crontab -l}. 
A default \cc{crontab} is saved in \cc{/home/cvgps/etc/crontab}. 

\section{Configuration file format \label{sConfigFileFormat}}

Configuration files use a common format and are plain text files, designed to be easily edited via a command-line
editor because in many applications, only shell access to the system will be available.

The file is usually divided into sections, with section names delimited by square brackets [ ]. Entries in each section
are of the form:
\begin{lstlisting}
key = value
\end{lstlisting}
For example,
\begin{lstlisting}
[Receiver]
manufacturer = Trimble
model = Resolution T
\end{lstlisting}
defines a section \cc{Receiver} and the two keys: \cc{manufacturer} and \cc{model}. 

The notation \cc{Section::Key} is used to fully specify keys. For example,
\cc{Receiver::model} and \cc{Receiver::manufacturer} specify the two keys above.

Keys and section names are not case-sensitive. In particular, the python and Perl libraries
which provide functions for reading the configuration files convert keys and section names to lower case.
The case of key values is preserved, since this may be signficant eg path names.

Leading and trailing whitespace is removed from keys, key values and section names.

Comments begin with a `\#'. 

Some keys define a list of sections. 
For example, the comma-separated list of values for \cc{CGGTTS::outputs} 
\begin{lstlisting}
[CGGTTS]
outputs = c1-code,p1-code,p2-code
\end{lstlisting}
defines three sections: \cc{c1-code}, \cc{p1-code}, and \cc{p2-code}.
This is a bodge which would be more elegantly addressed using an extensible format like XML, 
but it has proven to be sufficient for our needs.

\subsection{Paths} \label{s:ConfigFilePaths}

Paths to files  specified in a configuration file are constructed with the following 
precedence:
\begin{enumerate}
\item If the path begins with a leading slash, then it is interpreted as an absolute path
\item If a non-absolute path is specified, it is interpreted as being relative to 
	the users's home directory (or where the configuration file allows specification of a different root path eg in \hyperlink{h:rootpath}{gpscv.conf}, relative to that root path) 
\item Otherwise, the default path is used.
\end{enumerate}
Most software in OpenTTP follows these conventions.

\section{Data file formats \label{s:DataFileFormat}}

\subsection{GPS receiver}

This text file records messages from the GPS receiver. 
The native format of the messages can be a mix of ASCII and binary messages.
Binary messages are hexadecimal-encoded for saving in the log file. 
Some logging scripts record ancillary information, such as commands sent to the receiver. 
Comments in the log file are allowed, prefaced by a `\#' character. 
The `@' character is used to tag lines containing special information that needs to be parsed by
the processing software.

Messages are successive lines of the form:
\begin{lstlisting}
<message_id> <time_stamp> <message>
\end{lstlisting}
\textit{Example:}
\begin{lstlisting}
TO 00:00:02 cdfbc75a9a8c353fc5
\end{lstlisting}

Hex encoding of binary messages results in much larger files but these compress to a size not much larger
than the original binary data.

The exception to this is the Septentrio logging script, which uses the native SBF format.
Some logging scripts have the option of logging data in the receiver's native format, to facilitate
use of other tools.

\subsection{Time-interval counter \label{s:TICformat}}

This text file records the difference between GNSS receiver and the Reference Oscillator 1 pps,
measured each second. The convention is that the Reference oscillator provides the start trigger.
Entries are successive lines of the form:
\begin{lstlisting}
<time_of_day> <time_difference>
\end{lstlisting}
where the time difference is in seconds.\\
\textit{Example:}
\begin{lstlisting}
00:00:04  +4.0821E-006 
\end{lstlisting}

\input{srcs/gpscvconf}

\input{srcs/mktimetx}

\input{srcs/runmktimetx}

\input{srcs/mkcggtts}

\input{srcs/cnt9xlog}

\input{srcs/hp53131xlog}

\input{srcs/okxemlog}

\input{srcs/prs10log}

\input{srcs/ticclog}

\input{srcs/javad}

\input{srcs/nvs}

\input{srcs/septentrio}

\input{srcs/trimble}

\input{srcs/ublox}


\section{Miscellaneous tools}

\input{srcs/cggttsqc}

\input{srcs/cmpcggtts}

\input{srcs/editcggtts}

\input{srcs/editrnxnav}

\input{srcs/editrnxobs}

\input{srcs/fetchigs}

\input{srcs/ticqc}
