\section{lcdmonitor \label{slcdmonitor}}

\cc{lcdmonitor} runs the lcd display on the front panel of the  unit.

\cc{lcdmonitor} produces a log file \cc{/usr/local/log/lcdmonitor.log} that records 
significant commands run from  the front panel, for example reboots.

A lock file \cc{/usr/local/log/lcdmonitor.lock} is used to prevent duplicate processes from running.

\subsection{usage}
\cc{lcdmonitor} is automatically started by the system's init system.
On Debian, this is \cc{systemd}. It can be run manually for debugging purposes.

The command line options are:
\begin{description*}
	\item[-d]	run in debugging mode
	\item[-h]	print help and exit
	\item[-v]	print version information and exit
\end{description*}
To run \cc{ldcmonitor} on the command line, you will need to disable the entry in \cc{/etc/inittab},
reread the \cc{inittab} and kill any running \cc{lcdmonitor} process.

\subsection{configuration file}

The configuration file for \cc{ldcmonitor} is \cc{/usr/local/etc/lcdmonitor.conf}. This file is
only modifiable by the super-user. The file is divided into
sections, with section names delimited by square brackets [\space]. \\
\textit{Example:}
\begin{lstlisting}
token = value
\end{lstlisting}
Comments begin with a \cc{\#} character. Entries in the various sections of the configuration file
are given below. 

\subsubsection{[General] section}

{\bfseries NTP user}\\
This  defines the name of the user associated with NTP functions.\\
\textit{Example:}
\begin{lstlisting}
NTP user = ntp-admin
\end{lstlisting}

{\bfseries Squealer config}\\
This  specifies the location of the configuration file used by \cc{squealer}, a
program used to detect system problems.\\
\textit{Example:}
\begin{lstlisting}
Squealer config = /home/cvgps/etc/squealer.conf
\end{lstlisting}

\subsubsection{[UI] section}
{\bfseries Show PRNs}\\
This specifies whether or not to show the PRNs (or Space Vehicle identifiers) of
GPS satellites being tracked by the receiver. If this is set to zero, then only
the number of satellites tracked is displayed.\\
\textit{Example:}
\begin{lstlisting}
Show PRNs=1
\end{lstlisting}

{\bfseries LCD intensity}\\
This sets the intensity of the LCD display. Valid values are 0 to 100.\\
\textit{Example:}
\begin{lstlisting}
LCD intensity=90
\end{lstlisting}

{\bfseries LCD contrast}\\
This sets the contrast of the LCD display. Valid values are 0 to 100.\\
\textit{Example:}
\begin{lstlisting}
LCD contrast=95
\end{lstlisting}

\subsubsection{[GPSCV] section}
{\bfseries GPSCV user}\\
This  defines the name of the user associated with GPSCV functions.\\
\textit{Example:}
\begin{lstlisting}
GPSCV user = cvgps
\end{lstlisting}

{\bfseries gpscv config}\\
This defines the location of the file \cc{gpscv.conf}.\\
\textit{Example:}
\begin{lstlisting}
GPSCV config = /home/cvgps/etc/gpscv.conf
\end{lstlisting}

{\bfseries GPS restart command}\\
This specifies the command used to restart the GPS receiver. Note that since
\cc{lcdmonitor} runs as \cc{root}, the restart must be explicitly done
as \cc{cvgps}.\\
\textit{Example:}
\begin{lstlisting}
GPS restart command =su - cvgps -c '/home/cvgps/bin/check_rx'
\end{lstlisting}

{\bfseries GPS logger lock file}\\
This specifies location of the lock file used by the GPS logging process. It is
used to determine which process needs to be killed before a restart.\\
\textit{Example:}
\begin{lstlisting}
GPS logger lock file=/home/cvgps/logs/rx.lock
\end{lstlisting}

\subsubsection{[OS] section}
{\bfseries Reboot command}\\
This specifies the command used to reboot the PC.\\
\textit{Example:}
\begin{lstlisting}
Reboot command = /sbin/shutdown -r now
\end{lstlisting}

{\bfseries Poweroff command}\\
This specifies the command used to shut down the PC.\\
\textit{Example:}
\begin{lstlisting}
Poweroff command = /sbin/shutdown -t 3 -h
\end{lstlisting}

{\bfseries ntpd restart command}\\
This specifies the command used to restart \cc{ntpd}.\\
\textit{Example:}
\begin{lstlisting}
ntpd restart command = /sbin/service ntpd restart
\end{lstlisting}

\subsubsection{[Network] section}
{\bfseries DNS}\\
\textit{Example:}
\begin{lstlisting}
DNS = /etc/resolv.conf
\end{lstlisting}

{\bfseries Network}\\
\textit{Example:}
\begin{lstlisting}
Network = /etc/sysconfig/network
\end{lstlisting}

{\bfseries Eth0}\\
\textit{Example:}
\begin{lstlisting}
Eth0 = /etc/sysconfig/network-scripts/ifcfg-eth0
\end{lstlisting}

